COG-ED Manuscript

### 2022-05-30 06_Paper/COG-ED/Manuscript.Rmd
implemented comment 1.2.
implemented comment 2.1.
implemented comment 2.2

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - review & editing
      - Visualization
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role: 
      - Conceptualization
      - Funding acquistion
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
abstract: |
  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  One approach to quantify the SVs of levels of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
  Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
  We aim to replicate the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "~ 3,700"
bibliography      : CERED.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
always_allow_html : true
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}

@@

  here::i_am("flag_project_root_CERED.txt")

@@

With the present study, we alter one fundamental assumption of the original COG-ED paradigm: that the easiest *n*-back level has the highest SV.
We therefore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
Figure\ 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
Adding a comparison of 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding three more comparisons of the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
First, the SVs are still quite alike among levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels, and by starting each round with a choice between equal rewards.
For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
The level that was not chosen will be set to a fixed value of 2€.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks[@ScheffelZerna2022], we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al.[-@Westbrook2013].
Additionally, we will compare the effort discounting behavior of participants regarding the *n*-back task and an emotion regulation task.
The full results of the latter will be published in a second Registered Report[@ScheffelZerna2022].
The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.

@@

Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE*[@Greiner2015].
Participants will complete the personality questionnaires online and then visit the lab for two sessions one week apart.
NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Cacioppo1984; @Bless1994].
Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
The NFC scale shows comparably high internal consistency (Cronbach's $\alpha>.80$) [@Bless1994; @Fleischhauer2010].
Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session[@ScheffelZerna2022].
A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CERED).
In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
The paradigm starts with the *n*-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
After each level, participants fill out the NASA-TLX on a tablet.
Then, they complete the effort discounting procedure on screen, where each possible pairing of the four *n*-back levels is presented in a randomized order.
Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of *n*-back.
This is only done to incentivise truthful behavior in the effort discounting procedure, so the *n*-back data of this part will not be analyzed.
The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
The paradigm follows the same structure of task and effort discounting procedure, but participants can decide which strategy they want to reapply in the last block.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].

@@

The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at [github.com/ChScheffel/CERED](https://github.com/ChScheffel/CERED).

>>>>

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CAD paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - review & editing
      - Visualization
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role: 
      - Conceptualization
      - Funding acquistion
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
abstract: |
  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  One approach to quantify the SVs of levels of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
  Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
  We aim to replicate the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "~ 3,700"
bibliography      : CAD.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
always_allow_html : true
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}

@@

  here::i_am("flag_project_root_CAD.txt")

@@

With the present study, we alter one fundamental assumption of the original COG-ED paradigm: that the easiest *n*-back level has the highest SV.
We therefore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
Figure\ 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
Adding a comparison of 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding three more comparisons of the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
First, the SVs are still quite alike among levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels, and by starting each round with a choice between equal rewards.
For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
The level that was not chosen will be set to a fixed value of 2€.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks[@ScheffelZerna2022], we call it the Cognitive and Affective Discounting Paradigm (CAD).
In the present study, we will validate the CAD paradigm by conceptually replicating the findings of Westbrook et al.[-@Westbrook2013].
Additionally, we will compare the effort discounting behavior of participants regarding the *n*-back task and an emotion regulation task.
The full results of the latter will be published in a second Registered Report[@ScheffelZerna2022].
The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.

@@

Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE*[@Greiner2015].
Participants will complete the personality questionnaires online and then visit the lab for two sessions one week apart.
NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Cacioppo1984; @Bless1994].
Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
The NFC scale shows comparably high internal consistency (Cronbach's $\alpha>.80$) [@Bless1994; @Fleischhauer2010].
Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session[@ScheffelZerna2022].
A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CAD).
In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
The paradigm starts with the *n*-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
After each level, participants fill out the NASA-TLX on a tablet.
Then, they complete the effort discounting procedure on screen, where each possible pairing of the four *n*-back levels is presented in a randomized order.
Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of *n*-back.
This is only done to incentivise truthful behavior in the effort discounting procedure, so the *n*-back data of this part will not be analyzed.
After the computer paradigm, participants will fill out a short questionnaire on the tablet, indicating whether they have adhered to the instructions (yes/no) and what the primary motivation for their decisions during the ED procedure was (avoid boredom/relax/avoid effort/seek challenge/other).
The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
The paradigm follows the same structure of task and effort discounting procedure, but participants can decide which strategy they want to reapply in the last block.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].

@@

The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at [github.com/ChScheffel/CAD](https://github.com/ChScheffel/CAD).
